method

### 2021-08-27 06_Paper/ER-ED/method.Rmd
added text to 2.3 ER paradigm

The ER paradigm roughly consisted of two parts. 
Part one could be described as standard ER task that followed a block design (see Figure X), similar to paradigms previously used by our group [@Scheffel2021]. 
Participants were told to actively view neutral and negative pictures (see [2.4. Stimuli](##stimuli)) or to regulate all upcoming emotions by means of distraction, distancing and expressive suppression, respectively. 
Every participant first had the condition "active viewing-neutral" that served as a baseline condition.
During this block, 20 neutral pictures were presented.
Participants were asked to "actively view all pictures and permit all emotions that may arise."
In the second block, participants actively viewed negative pictures.
During the third, fourth, and fifth block, participants saw negative pictures and were asked to regulate their emotions using distraction, distancing, and suppression.
In order to achieve distraction, participants were asked to think of a geometric object or an everyday activity, like brushing their teeth.
During distancing, participants were asked to "take the position of a non-involved observer, thinking about the picture in a neutral way."
Participants were told not to re-interpret the situation or attaching a different meaning to the situation.

>>>>

The ER paradigm roughly consisted of three parts that will be described in the following.

_Part one: ER task._ <br>
Part one could be described as standard ER task that followed a block design (see Figure X), similar to paradigms previously used by our group [@Scheffel2021]. 
Participants were told to actively view neutral and negative pictures (see [2.4. Stimuli](##stimuli)) or to regulate all upcoming emotions by means of distraction, distancing and expressive suppression, respectively. 
Every participant first had the condition "active viewing-neutral" that served as a baseline condition.
During this block, 20 neutral pictures were presented.
Participants were asked to "actively view all pictures and permit all emotions that may arise."
In the second block, participants actively viewed negative pictures.
During the third, fourth, and fifth block, participants saw negative pictures and were asked to regulate their emotions using distraction, distancing, and suppression.
In order to achieve distraction, participants were asked to think of a geometric object or an everyday activity, like brushing their teeth.
During distancing, participants were asked to "take the position of a non-involved observer, thinking about the picture in a neutral way."
Participants were told not to re-interpret the situation or attaching a different meaning to the situation.
During suppression, participants were told to "suppress their emotional facial expression."
They should imagine being observed by a third person that should not be able to tell just by looking at the facial expression whether the person is looking at an emotional picture.
Participants were instructed not to suppress their thoughts or change their facial expression to the opposite [@Scheffel2021].
All participants received written instruction and completed a training session.
After the training session, participants were asked about their applied ER strategies to avoid misapplication.
The order of the three regulation blocks (distraction, distancing, and suppression) was randomized between participants.

_Part two: ER effort discounting._ <br>
In the second part, ER effort discounting took place.
Each possible pairing of strategies (distraction vs. distancing, distraction vs. suppression, and distancing vs. suppression) was presented in a randomized order.
Participants were instructed to decide as realistically as possible, imaging the displayed money would really be up for election.

_Part three: ER choice._ <br>
